You have more money in your wallet. Does that mean you will spend extra on food?

### 2024-04-06 paper/paper.qmd
updated datasheet file

---
title: "You have more money in your wallet. Does that mean you will spend extra on food?"
subtitle: "I analyze the relationship between disposable income and food expenditure for American consumers"
author: Ahnaf Alam
thanks: "Code and data are available at https://github.com/AhnafAlam1/income_and_expenditure/tree/main"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
toc: true
---

@@

*Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.8

>>>>

---
title: "You have more money in your wallet. Does that mean you will spend extra on food?"
subtitle: "I analyze the relationship between disposable income and food expenditure for American consumers"
author: Ahnaf Alam
thanks: "Code and data are available at https://github.com/AhnafAlam1/income_and_expenditure"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
toc: true
---

@@

*Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
